---
# PDF v1.1 FINAL
title: "Virginia WMA eBird Species Report"
output:
  pdf_document:
    latex_engine: xelatex
geometry: margin=1in
header-includes:
  - \usepackage{titling}
  - \usepackage{fontspec}
  - \IfFontExistsTF{Georgia}{\setmainfont{Georgia}}{\setmainfont{TeX Gyre Termes}}
  - \setlength{\droptitle}{-0.85in}
  - \pretitle{\begin{center}\LARGE}
  - \posttitle{\par\end{center}\vspace{-0.5in}}
params:
  site_name: ""
  selected_year: ""
  selected_species: ""
  checklist_total: 0
  species_individuals: 0
  species_checklists: 0
  annual_plot_path: ""
  map_path: ""
  report_date: ""
  heat_metric: ""
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

\begin{center}
\section*{Report Summary}
\vspace{-0.15in}
\textbf{Generated:} `r params$report_date`
\end{center}

\begin{center}
\begin{minipage}[t]{0.85\textwidth}
\centering

\begin{minipage}[t]{0.45\textwidth}
\raggedright
\textbf{Site:} `r params$site_name`  

\textbf{Year:} `r ifelse(params$selected_year == "", "None", params$selected_year)`  

\textbf{Checklists:} `r format(params$checklist_total, big.mark = ",")`
\end{minipage}
\hfill
\begin{minipage}[t]{0.53\textwidth}
\raggedright
\textbf{Selected Species:} `r ifelse(params$selected_species == "", "None", params$selected_species)`  

\textbf{Individuals:} `r format(params$species_individuals, big.mark = ",")`  

\textbf{Unique Checklists:} `r format(params$species_checklists, big.mark = ",")`
\end{minipage}

\end{minipage}
\end{center}

\vspace{0.1in}

\begin{center}
{\large \textbf{Map Based on `r if (params$heat_metric == "all_checklists") {
  "All Checklists"
} else if (params$heat_metric == "individuals_density") {
  paste("Individual Density (", params$selected_species, ")", sep = "")
} else if (params$heat_metric == "species_density") {
  paste("Species Density (", params$selected_species, ")", sep = "")
} else {
  "Points"
}`}}
\end{center}

```{r map-plot, fig.align='center', out.width='98%'}
if (file.exists(params$map_path)) {
  knitr::include_graphics(params$map_path)
}
```

\begin{center}
{\small Data based on 2/2026 EBD}
\end{center}

\newpage

\begin{center}
{\large \textbf{Checklists Over Time}}
\end{center}

```{r annual-plot, fig.align='center', out.width='98%'}
if (file.exists(params$annual_plot_path)) {
  knitr::include_graphics(params$annual_plot_path)
}
```